\LARGE \bf Grasp Metric for Shape Uncertainity with Gaussian Proccess Implicit Surface Representation (Not Finished Work)

### 2014-07-17 paper.tex
Edited intro a lot

We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
We assume friction is at the contact points. 
The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
%\section{Goals and Current Progress}
We are working to extend this metric to incorporate shape uncertainty.
For our grasping model, we make a simplifying assumption that each gripper approaches the object along a fixed line of action and thus the contact points lie on this line.
We would like to analyze the induced distributions over grasp parameters and the Ferrari-Canny metric.
Specifically, we would like to answer the following question:
What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
%We use recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical}, and prove a tight probabilistic bound on the change in grasp quality under shape uncertainty.
%We also provide an efficient way to calculate the distributions on the grasp parameters and include a way to update them quickly with new observations.

>>>>

We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape.
We assume friction is at the contact points. 
The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.
%\section{Goals and Current Progress}
We are working to extend this metric to incorporate shape uncertainty.
For our grasping model, we make a simplifying assumption that each gripper approaches the object along a fixed line of action and thus the contact points lie on this line.
We would like to analyze the induced distributions over grasp parameters and the Ferrari-Canny metric.
Specifically, we would like to answer the following question:
What is the probability of achieving force closure under the given grasp approach directions and implicit surface distribution?
So far, we have explicit formulas for the distributions of the contact points along the line of action and surface normal vectors and the expected center of mass of the object to be grasped.
We are thoroughly investigating utilizing recent results on a Lipschitz constant for the Ferrari-Canny metric \cite{pokorny2013classical} in order to prove probabalistic bounds on the change in grasp quality under shape uncertainty.
We are also investigating efficient ways to calculate the distributions on the grasp parameters and ways to update them quickly with new observations.
